Pesticides in small agricultural streams in Germany

### 2016-08-19 article.tex
test

\subsection{Representativeness of the dataset}
The compiled dataset of governmental monitoring data represents currently the most comprehensive one available for Germany.
Similar nationwide datasets have been compiled for the Netherlands \citep{vijver_spatial_2008}, Switzerland \todo{cite munz} and the United States (Water Quality Portal (WQP) \url{www.waterqualitydata.us}).

@@

Nevertheless such nationwide compilations, may not only be useful for governmental surveillance, but also to answer other questions, like validation of exposure modeling \todo{cite knäbel?}, retrospective evaluation of regulatory risk assessment \citep{knauer_pesticides_2016,stehle_pesticide_2015}, investigation of pesticide mixtures \todo{cite schreiner} or scientific research.

% current problems in monitoring and possible solutions
A nationwide assessment is hampered \todo{check verb} by the inhomogeneity of monitoring data between federal states:
There are not only big differences in the spatial distribution and quantity of sampling sites (Figure \ref{fig:fig1}), but also the spectrum of analyzed compounds (Figure \ref{fig:fig2}) and differences in the quality of chemical analyses.
Future monitoring programs should aim at resolving these differences in order to enable a nationwide assessment.

@@

@@

% Conclusions
Exceedances of RACs are undesirable

>>>>

\subsection{Representativeness of the dataset}
The compiled dataset of governmental monitoring data represents currently the most comprehensive one available for Germany.
Similar nationwide datasets have been compiled for the Netherlands \citep{vijver_spatial_2008}, Switzerland \citep{munz_pestizidmessungen_2011} and the United States (Water Quality Portal (WQP) \url{www.waterqualitydata.us}).

@@

Nevertheless, such nationwide compilations, may not only be useful for governmental surveillance, but also to answer other questions, like validation of exposure modeling \cite{knabel_fungicide_2014}, retrospective evaluation of regulatory risk assessment \citep{knauer_pesticides_2016,stehle_pesticide_2015}or investigation of pesticide mixtures \cite{schreiner_pesticide_2016}.

% underestimation grab sampling

% current problems in monitoring and possible solutions
A nationwide assessment of pesticide pollution is hampered by the inhomogeneity of monitoring data between federal states:
There are not only big differences in the spatial distribution and quantity of sampling sites (Figure \ref{fig:fig1}), but also the spectrum of analyzed compounds (Figure \ref{fig:fig2}) and differences in the quality of chemical analyses.
Future monitoring programs should aim at resolving these differences in order to enable a nationwide assessment.

@@

% all detects for neonics > RAC => need to lower LOQs!+-

@@

% WFD 10km² 0> brauchen auch kleinere.

% Conclusions
Exceedances of RACs are undesirable ...
